Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-17 introduction.tex
Word choice
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1090 ccdd05d5-56c1-461a-bf98-85f6876523b4

It is infeasible to search this large an area for a prompt counterpart. For
reference, \textsc{lsst} should see first light around the same time as
Advanced \LIGO{} and will have an unparalleled field of view of 9.6 deg$^2$
\citep{2008arXiv0805.2366I}.  However, if we can take galactic luminosities
to accurately trace mass and thus proxy for the \CBC{} event rate, it is
possible to reduce the localization uncertainty using a galaxy catalog, along
with the sky location and luminosity distance estimate from the \GW{} signal,
as a prior probability distribution \citep{galaxy-catalog} as was done in
S6/VSR3. Within the expected Advanced \LIGO{} \textsc{ns}--\textsc{ns} horizon
distance, the number of galaxies that can produce a given signal
amplitude is much larger than the number for initial \LIGO{} and thus the
catalog will not be as useful for downselecting pointings generally. However,
sources that are detectable before merger are likely to be exceptionally
nearby. Thus there will be fewer galaxies to consider for a given
early-warning candidate and catalog completeness will be less of a concern.
This should allow us to shrink the 90\% confidence area substantially.
Even so, it will be desirable to mobilize a large number of heterogeneous
telescopes in order to guarantee imaging this exceptional event at the instant
of merger. Because the sky localization will improve rapidly until merger,
by the time that the entire \CBC{} event is over it will be
possible to send a second alert to downselect the images that have already been
taken as well as repoint telescopes to more likely locations.

>>>>

It is infeasible to search this large an area for a prompt counterpart. For
reference, \textsc{lsst} should see first light around the same time as
Advanced \LIGO{} and will have an unparalleled field of view of 9.6 deg$^2$
\citep{2008arXiv0805.2366I}.  However, if we can take galactic luminosities
to accurately reflect mass and thus be a proxy for the \CBC{} event rate, it is
possible to reduce the localization uncertainty using a galaxy catalog, along
with the sky location and luminosity distance estimate from the \GW{} signal,
as a prior probability distribution \citep{galaxy-catalog} as was done in
S6/VSR3. Within the expected Advanced \LIGO{} \textsc{ns}--\textsc{ns} horizon
distance, the number of galaxies that can produce a given signal
amplitude is much larger than the number for initial \LIGO{} and thus the
catalog will not be as useful for downselecting pointings generally. However,
sources that are detectable before merger are likely to be exceptionally
nearby. Thus there will be fewer galaxies to consider for a given
early-warning candidate and catalog completeness will be less of a concern.
This should allow us to shrink the 90\% confidence area substantially.
Even so, it will be desirable to mobilize a large number of heterogeneous
telescopes in order to guarantee imaging this exceptional event at the instant
of merger. Because the sky localization will improve rapidly until merger,
by the time that the entire \CBC{} event is over it will be
possible to send a second alert to downselect the images that have already been
taken as well as repoint telescopes to more likely locations.
